More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-04-09 2016-Weak-FH-Bisim/WeakBisim.tex

 \smallskip
 $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {Prot_1 \OTarrow{\tau} Prot_2}
    $

    \smallskip
    Here the global states $Prot_1$ and $Prot_2$ encode the states of
    the 4 pLTS composing the system, namely
    $Prot_1=\ostate{s_1,m_0,m_0,r_0}$ and
    $Prot_2=\ostate{s_2,m_1,m_0,r_0}$, showing that the sender and the
    first medium have evolved during this transition.
    The predicate $Pred$ involves the state variables $s_1\_m$ and
    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
    state variables of the medium.

 \smallskip
 $  OT_1  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
%                            \xrightarrow{in(?m,?b)}_{M1}
      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
    $

    \smallskip
    The global states $ABP_1$ and $ABP_2$ have the same structure than
    $Prot_1$ and $Prot_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.
\end{example}

@@

>>>>

@@

 \smallskip\noindent
 $  OT_2  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
   %                           \xrightarrow{in(?m,?b)}_{M1}
      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb, v=\tau];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{v} \ostate{s_2,m_1,m_0,r_0}}
    $

    \smallskip
    Note that the global states shows how the sender and the
    first medium have evolved during this transition, the sender
    moving from $s_1$ to $s_2$, and the first (forward) medium from
    $m_0$ to $m_1$.
    The predicate $Pred$ involves the state variables $s_1\_m$ and
    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
    state variables of the medium.

 \smallskip\noindent
 $  OT_1  = \openrule{
%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
%                            \xrightarrow{in(?m,?b)}_{M1}
      \{\xrightarrow{b_P}_P\}; Pred=[b_P=send(m)\land v=\underline{send(m)}]; Post=\{s1\_m:=m\}
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{v} \ostate{s_1,m_0,m_0,r_0}}
    $

    \smallskip
    The global states here have the same structure than
    in $OT\_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.
\end{example}
